---
title: "Task2"
author: "Kirill Tumanov"
date: "04 10 2019"
output: 
  html_document:
    theme: journal
    highlight: haddock
    toc: true
    toc_float: false
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plyr)
library(rvest)
```
#Task

How many companies have been registered per month, per county in 2019?
```{r}
url <- read_html ("https://w2.brreg.no/kunngjoring/kombisok.jsp?datoFra=01.01.2019&datoTil=25.09.2019&id_region=100&id_fylke=-+-+-&id_niva1=2&id_bransje1=0")
#make a table
data_prep <- html_nodes(url, xpath = "//table")
data01 <- as.data.frame(html_table(html_nodes(data_prep, "table"))) 
```

## Cleaning Data in R
```{r}
#variables
names(data01) <- c("x1","company","county","number","x3","date","x4","type","x5")
data01 <- data01[,c("company","county","number","date","type")]
```

#Sort by 3 counties
```{r}
#create rows for counties
nord_row <- which(grepl("Nordland", data01$county))
troms_row <- which(grepl("Troms", data01$county))
fin_row <- which(grepl("Finnmark", data01$county))
data01$county[c(nord_row:troms_row-1)] <- "Nordland"
data01$county[c(troms_row:fin_row-1)] <- "Troms"
data01$county[c(fin_row:nrow(data01))] <- "Finnmark"
#delete excess lines
data01 <- data01[-c(1:6,1060,1061,1814,1815,2227), ]
```

#Format
```{r}
data01 <- data01 %>%
  mutate (date = as.Date(date,format("%d.%m.%Y")))
#delete "Rettelse av foretaksnavn"
data01 <- data01[!data01$type=="Rettelse av foretaksnavn",]
```

#Preparing for a plot
```{r}
#make a comfortable format for date
  data02 <- data01 %>%
  mutate(month = lubridate::month(date)) %>%
  mutate(month = paste0("2019","-",month,"-","01")) %>%
  mutate(month = lubridate::ymd(month)) %>%
  ddply(c("county", "month"), summarise, amount=as.numeric(length(company)))

```

##Plot
```{r}
data02 %>%
  ggplot(aes(x=month,y=amount, color=county, group=county)) +
  facet_grid(~county) +
  geom_point() +
   geom_line() +
  labs(x = "Months in 2019", y = "Number of new companies", title = "Amount of new companies registered per month, per county in 2019") +
scale_y_continuous(limits =  c(0,150),
                     breaks=seq(0, 150, by = 20))
```

#Total amount of companies
```{r} 
data02 %>%
  group_by(county) %>%
  summarise(total=sum(amount))
```


Graph shows how many comapnies have been registered per month in Finmark, Nordland and Troms in 2019. The smallest number of companies were registered in Finmark and the biggest amount of companies were registered in Nordland, Troms county is located at the 2-nd place between these 3 counties. During 2019, 2206 companies were registered in these 3 counties.
